Implementing Distributed Systems Directly with I/O Automata in Ioa++

### 2011-09-13 papers/paper1/programming_model.tex
ioa::automaton is virtual base.

In this section, we show how I/O automata can be used to construct programs by implementing an algorithm for electing a leader in a unidirectional ring.
The algorithm we consider is the asynchronous LCR algorithm presented by Lynch in Chapter 15 of~\cite{lynch1996distributed} which is in turn based on the work of LeLann~\cite{le1977distributed} and Chang and Roberts~\cite{chang1979improved}.
The LCR algorithm assumes that every node has a unique identifier (UID).
When the protocol begins, each node sends its UID to its successor.
When a node receives a UID from its predecessor that is greater than its own UID, it forwards the UID to its successor.
When a node receives its own UID, it elects itself the leader of the ring.

>>>>

In this section, we show how I/O automata can be used to construct programs.

We motivated our presentation using the classic problem of electing a leader in a unidirectional ring.

\paragraph{Leader election in a unidirectional ring.}

 by implementing an algorithm for electing a leader in a unidirectional ring.
The algorithm we consider is the asynchronous LCR algorithm presented by Lynch in Chapter 15 of~\cite{lynch1996distributed} which is in turn based on the work of LeLann~\cite{le1977distributed} and Chang and Roberts~\cite{chang1979improved}.
The LCR algorithm assumes that every node has a unique identifier (UID).
When the protocol begins, each node sends its UID to its successor.
When a node receives a UID from its predecessor that is greater than its own UID, it forwards the UID to its successor.
When a node receives its own UID, it elects itself the leader of the ring.
